A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-07-11 src/paper.tex
WIP: Web application

The front controller architectural design pattern~\cite{Buschmann2007} is employed to centralize requests processing in a single component. Each second screen client sends requests to and receives responses from a single URL, what simplifies application development.

- Web application

>>>>

\subsection{Web Application}
\label{ssub_web_application}

The web applications can be hosted in the AHI

The requests handling is carried out by using the front controller architectural design pattern~\cite{Buschmann2007}. It is employed to centralize requests processing in a single component, which facilitates the design and implementation of services for different clients. As a result, client applications developed for different operating systems and send requests to and receive response from a single URL.
